paper1_figures

### 2024-01-08 scoping_review_short.Rmd
final 3rd version - 08.01.24

Commons can assume various forms, because "they can arise whenever a community decides it wishes to manage a resource in a collective manner, with a special regard for equitable access, use and sustainability" [@Bollier2014, p.19]. The variety of definitions can be resumed through three key points. First, commons allow to manage shared resources [@Ostrom1990] and to find solution for shared needs of the population [@Euler2018; @Euler2019]. Second, commons are managed by a self-organized community of users [@Ostrom1990], i.e. the commoners. This community is a "social network of mutual aid, solidarity, and practices of human exchange that are not reduced to the market form" [@DeAngelis2003, p.1]. Moreover, commoners' organization is usually local, egalitarian, integrative, and fair [@Gidwani2011]. Third, the community's social practices are called "commoning" and, thanks to this process, commoners create institutions to govern the commons [@Euler2018; @Schmelzer2022]. Finally, although commons are often thought just as a shared resource, the other two aspects are also essential in defining them. Therefore, it is important to consider the commons as the integration of the resource, the community (i.e. the commoners) and its social practices (i.e. commoning) [@Bollier2014]. For this reason, it is essential to have a closer look at the individuals who are part of commons.

@@

Despite its importance, cooperation has not been much investigated in commons scientific literature. At the same time, other disciplines such as psychology extensively studied it. More specifically, social dilemma experiments allowed to identify several factors that impact cooperation [e.g. @VanLange2013]. For this reason, the current scoping review is aimed at gaining insight into cooperation in commons through social dilemma literature. In the next section, we give an overview about the existing research about cooperation in commons, afterwards we will detail the research questions.

@@

However, research in different disciplines has convincingly demonstrated that people can engage in collective actions to sustainably manage shared resources, thus falsifying Hardin's predictions [@Poteete2010a]. Among these studies, the most important is Elinor Ostrom's seminal work [-@Ostrom1990], where she studied several real-life commons, some of them successfully managed by the community of users without the intervention of an external authority. Based on her observations, she established seven design principles that are present in all the successful commons, plus an eighth one for more complex cases.[^2]

@@

The first principle posits that boundaries are essential: it must be clear which is the shared resource, and who can benefit from it, otherwise, "no one knows what is being managed or for whom" (p. 91). Second, the rules must be congruent with the local conditions, i.e. they must reflect the specific attributes of the particular resource. Thirdly, individuals affected by the rules must be able to participate in modifying them. This ensure that the rules fit well to the local conditions and allows to promptly adapt them when needed. The fourth and fifth principles concern a monitoring and a graduate sanction system. Interestingly, these systems are successfully implemented by commoners themselves, with no need of an external institution. In fact, in order to know that the best strategy is to follow the rules, one must be sure that the others are also complying to them. For this reason, it is in everybody's self-interest to monitor other commoners. Similarly, the graduate sanction system can be easily self-regulated: even if punishing is usually profitable for the punisher, fines are naturally small for the first infraction and get higher only if the person persists in breaking the rules. In fact, since infractions are often due to extreme situations, punishers tend to be sympathetic because it could happen to them too. Linked to the previous principle, the sixth posits that people must have access to low-cost conflict resolution mechanisms, since, in a situation like a commons, disagreements between members are inevitable. Conflict resolution arenas give the rule-breaker the possibility to explain the mistake, and ensure that compliance to rules does not drop after every infraction. Finally, according to the seventh principle, external authorities should not challenge the commoners' right to self-organize and should recognize the commons' institutions.

@@

Secondly, on the experimental level, the laboratory study of social dilemmas also largely contributed to the investigation of cooperation, by identifying several factors that impact it [e.g. @VanLange2013]. A typical constellation in these experiments (often also referred as "public good games" or "common resource experiments") is that people face a conflict between personal and collective interest. Each individual obtains a higher personal payoff with a non-cooperative, self-interested behaviour than with a social, cooperative one, independently from what others do. At the same time, everybody's payoff is higher if all cooperate than if all defect [@Dawes1980]. Social dilemma experiments are very useful for gaining insight into cooperation, because they are easily implemented in a laboratory, and provide a standard experimental paradigm to test under which conditions people cooperate [@Balliet2011]. In general, these studies demonstrated that people are able to cooperate, and that their behaviour is impacted by variables that should not play a role from a rational point of view [@Ostrom1998].

@@

Based on this evidence, the current paper synthesizes existing research about cooperation in social dilemmas, to provide a set of factors that impact cooperative behaviours in commons. This work will therefore lay the foundations to implement experimental and quantitative studies in real-life commons, which, in turn, will allow to gain insights about cooperation beyond artificial laboratory settings.

@@

<!--# PROBLEM: all my research questions are about social dilemmas, and the idea was to use this litterature to better understand cooperation in commons, however I also included papers that studied commons (in the search, one of the key words was "commons" => solution (?): in the methods section say that I also included commons literature for X,Y reasons (more completeness? see the rapport between the amount of SD and commons studies?) -->

@@

<!--# add somewhere that qualitative studies are ok? -->

@@

Our analysis identified five individuals factors that impact cooperation: gender, social status, group identification, values and personality traits, and trust. In the following sections, we describe their principal effects on cooperation, and provide an overview of the moderators of each effect presented in the reviewed papers. A resume of the different individual factors is provided in Table 2, while more details about moderators are included in Appendix A.

<!--# in the text: tables with the name of factor, the papers, the main effect and a list of moderatorsin Annexe: same table, but with more details for each moderator effect is it useful to put in both tables the analyzed papers for each factor?for the word count: useful to put all the authors just in the Annexe table, and in the text letting only N=11-->

+---------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+------------------------------------------------------------------+

@@

+===============================================================+==========================================================================================================================================================================================+=================================================================================================+==================================================================+
| Gender                                                        | *N*=11\                                                                                                                                                                                  | Ambiguous                                                                                       | -   Other participants' characteristics                          |
|                                                               | @Dorrough2019; @Peshkovskaya2017; @Balliet2011; @Spadaro2023; @Sell2009; @Gomez-Ruiz2020; @Colman2018; @Peshkovskaya2019; @Barrero-Amortegui2021; @Simpson2003; @Irwin2015               |                                                                                                 | -   Group composition                                            |

@@

+---------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+------------------------------------------------------------------+

@@

|                                                               | @Aksoy2019; @Kingsley2016; @VanLange2013; @Chen2022; @Camera2020; @VanKlingeren2021                                                                                                      |                                                                                                 | -   Group composition                                            |
+---------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+------------------------------------------------------------------+

@@

|                                                               | @Arora2016; @Noonan2016; @Gomez-Ruiz2020; @VanVugt2009; @Zhang2019; @Chen2007; @Wit1992; @Dorrough2015; @Aksoy2019; @Puurtinen2009; @Nockur2020; @Kramer1984; @Jackson2011; @Jackson2012 |                                                                                                 | -   Intergroup competition                                       |

@@

+---------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+------------------------------------------------------------------+
| Social Value Orientation and other values/personality factors | *N*=5 (SVO)\                                                                                                                                                                             | Pro-social individuals cooperate more than pro-self                                             | -   Incentives                                                   |
|                                                               | @Balliet2009; @Emonds2011; @VanLange1998; @DeKwaadsteniet2008; @Lu2019                                                                                                                   |                                                                                                 | -   Uncertainty about the number of members                      |
|                                                               |                                                                                                                                                                                          | Pro-environmental values are positively correlated to cooperation                               | -   Deliberation                                                 |
|                                                               | *N*=9 (other factors)\                                                                                                                                                                   |                                                                                                 | -   Inter- vs independent self                                   |
|                                                               | @Sussman2016; @Fosgaard2019; @Kieslich2014; @Hilbig2018; @Kocher2017; @Schlosser2018; @Liu2009a; @Probst1999; @Chen2007                                                                  | Left-wingers are more cooperative than right-wingers                                            | -   Perceived social norms                                       |

@@

+---------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+------------------------------------------------------------------+
| Trust                                                         | *N*=10\                                                                                                                                                                                  | People with high levels of trust cooperate more than people with low levels                     | -   Degree of conflict between personal and collective interests |
|                                                               | @Balliet2013; @Lubke2021; @VanLange2013; @Kocher2015; @Smith2013; @Chaudhuri2002; @Oyediran2018; @Sturm2019; @Franzen2019; @Rompf2017                                                    |                                                                                                 | -   Uncertainty about others' intentions                         |

@@

On the group level, we identified four factors from the reviewed papers: incentives, communication, social norms and anonymity. As for the individual factors, in the following sections we detail the main effects of each factor, and we provide an overview of possible moderators. A remsume of the main effects can be found in Table 3, while more details about the moderators in Appendix A.

+-----------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+
| Organizational factor | Analyzed papers                                                                                                                                                                                                                                                  | General effect on cooperation                                                  | Moderators                                                    |
+=======================+==================================================================================================================================================================================================================================================================+================================================================================+===============================================================+
| Incentives            | *N*=18\                                                                                                                                                                                                                                                          | Punishment and reward systems have a positive effect on cooperation            | -   Cost of implementation                                    |
|                       | @Balliet2011a; @VanDijk2015; @Pfattheicher2018; @Nockur2021; @Egas2008; @Milinski2012; @Kingsley2016; @Chen2022; @Xiao2016; @Rockenbach2019; @VanDijk2015; @VanVugt2009; @Schlosser2018; @Irwin2014; @Mulder2006; @Jacquet2011; @Nelissen2013; @Maier-Rigaud2010 |                                                                                | -   Type of interaction                                       |
|                       |                                                                                                                                                                                                                                                                  |                                                                                | -   Other participants' characteristics and group homogeneity |
|                       |                                                                                                                                                                                                                                                                  |                                                                                | -   Context                                                   |
|                       |                                                                                                                                                                                                                                                                  |                                                                                | -   Organization                                              |
|                       |                                                                                                                                                                                                                                                                  |                                                                                | -   Type of incentives                                        |
+-----------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+
| Communication         | *N*=11\                                                                                                                                                                                                                                                          | Having the possibility to communicate with other members increases cooperation | -   Group size                                                |
|                       | @Balliet2010; @Bicchieri2002; @Janssen2014; @Koessler2021; @Adams2022; @Hopthrow2005; @Kumakawa2013; @Torsvik2011; @Feinberg2014; @Feinberg2012; @Giardini2021                                                                                                   |                                                                                | -   Type of communication                                     |
|                       |                                                                                                                                                                                                                                                                  |                                                                                | -   Content                                                   |
|                       |                                                                                                                                                                                                                                                                  |                                                                                | -   Timing                                                    |
+-----------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+
| Social norms          | *N*=8\                                                                                                                                                                                                                                                           | Cooperative social norms increase cooperation                                  | -   Anonymity                                                 |
|                       | @VonBorgstede2018; @Thogersen2008; @Rege2004; @Arora2012; @VanLange2013; @Bardsley2005a; @Weber2008; @Bicchieri2002                                                                                                                                              |                                                                                |                                                               |
+-----------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+
| Anonymity             | *N*=10\                                                                                                                                                                                                                                                          | Individuals cooperate more in non-anonymous situations than in anonymous ones  | -   Personal costs and benefits                               |
|                       | @Wang2017; @Rege2004; @VanVugt2010a; @Butz2021; @Romano2016; @VonBorgstede2018; @Jiang2021; @Mosler1993; @Przepiorka2020; @Koessler2021a                                                                                                                         |                                                                                |                                                               |
+-----------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+

@@

### Social Norms

@@

The second identified factors is social status, and, once again, we obtained contradictory findings about its effect on cooperation. However, our analysis revealed that members of low-status groups show solidarity with other low-status individuals, while this does not happen in high-status groups. This is consistent with the existing literature on social status. First, there are structural differences between high- and low-status group's dynamic, that make high-status members more individualistic than low-status [@Lorenzi-Cioldi2002]. Second, high-status individuals display more system justification (i.e. they perceive the social system as fair) and more Social Dominance Orientation (i.e. they have a preference for inequality between social groups) than low-status [@Caricati2012; @Vargas-Salfate2018]. This is negatively correlated with concern about others and altruism [@Pratto1994]. For this reason, social status must also be taken into account when investigating cooperation, since the solidarity dynamics described above influence individuals' behaviours.

Third, we found a strong positive effect of social identification: the more individuals identify with their group, the more they are likely to act for the group's good. <!--# question: when I recall results in the discussion, do I need to put again the citations? --> This is in line with the Social Identity Theory [@Tajfel1974], which posits that people's identity is also composed by their group affiliations. Therefore, the strongest the identification with a group, the more personal interests are aligned with group's ones. Also, within a social group, individuals perceive themselves as more similar to other members, and therefore they are more susceptible to adopt collective goals and behaviours [@Turner1984; @Fritsche2018]. Thus, for a group's success, its members' identification is essential: for instance, strongly identified individuals are less likely to leave a group in case of failure or difficulties [@Ellemers1997]. Given its importance, strengthen the commoners' social identification could significantly improve their cooperation for the commons' good. Moreover, priming a common social identity is quite simple [e.g. @Kramer1984; @Zhang2019]: therefore, this could allow to enhance cooperation in an easy and cheap way.

Fourth, Social Value Orientation also impacts cooperation. More specifically, individuals with a pro-social orientation cooperate more than those pro-self oriented. In fact, pro-social value more equality in outcomes, while for pro-self is the personal gain which is more important [@VanLange1999]. In addition to SVO, there are other values and personality traits which impact cooperation, such as political orientation, justice sensitivity, and self-control. Interestingly, although personality trait are usually stable, it is possible to modify values and attitudes, for example by making the participant elaborate about them [@Petty1995]. This technique could therefore be used to improve cooperation in commons.

@@

<!--# in the precent version I did not have a specific research question about how factors are connected to each-other, so this part fitted well: I took the results and completed them with related literatureHowever, now that I do have a research question about the moderation, it feels strange to add new results in this part. Should I take here only the moderation effects identified in the results section? Or maybe should I start from what I found to further develop on other moderators? -->

@@

Concerning the review's limitations, we could identify three. First, there is a lack of representation of the global population. In fact, two thirds of the analyzed papers were studies conducted in Europe or in North America, and the fourteen reviews included were also mostly based on studies from occidental countries. The current results apply therefore to Western societies and should not be generalized to other cultures. In fact, there are cultural differences in individualism and collectivism: generally, North American and European cultures are more individualistic, while South American, African and Asian ones are more collective [@Triandis1989]. These differences affect the extent to which individuals define themselves as part of a group [@Trafimow1991] and, consequently, their behavior in cooperative situations [e.g. @Kuwabara2014]. It is therefore likely that, in different cultures, cooperation relies on different mechanisms: comparative studies between this two regions should be conducted in order to reach a global understanding of cooperation.

Secondly, our aim was to use results of social dilemma researches to gain a better understanding of commons, therefore most of the included studies had a laboratory setting. In fact, this kind of setting is very useful to study social dilemmas because it provides a standard paradigm [@Balliet2011]. However, this does not allow to exactly reproduce the dynamics of a commons [@Henry2011; @Cole2010]: some elements such as cultural factors and specific conditions affecting the decision-making process cannot be reproduced in lab experiments [@Janssen2015]. Therefore, this paper offers a good basis about elements influencing cooperation in commons, but future studies should confirm these results in real-life settings. Moreover, this review is not informative about the relative importance of each factor. To shed light on this topic, quantitative studies are needed.

@@

In conclusion, a successful commons relies on the cooperation of its members, but this topic has not yet been extensively studied. Thus, further researches are needed to address the limitations of the current review and to reach a deeper understanding of this topic.

>>>>

Commons can assume various forms, because "they can arise whenever a community decides it wishes to manage a resource in a collective manner, with a special regard for equitable access, use and sustainability" [@Bollier2014, p.19]. The variety of definitions can be resumed through three key points. First, commons allow to manage shared resources [@Ostrom1990] and to find solution for shared needs of the population [@Euler2018; @Euler2019]. Second, commons are managed by a self-organized community of users [@Ostrom1990], i.e. the commoners. This community is a "social network of mutual aid, solidarity, and practices of human exchange that are not reduced to the market form" [@DeAngelis2003, p.1]. Moreover, commoners' organization is usually local, egalitarian, integrative, and fair [@Gidwani2011]. Third, the community's social practices are called "commoning" and, thanks to this process, commoners create institutions to govern the commons [@Euler2018; @Schmelzer2022]. Finally, although commons are often thought just as a shared resource, the other two aspects are also essential in defining them. Therefore, it is important to consider the commons as the integration of the resource, the community (i.e. the commoners) and its social practices (i.e. commoning) [@Bollier2014]. It is therefore essential to have a closer look at the individuals who are part of commons.

@@

Despite its importance, cooperation has not been much investigated in commons scientific literature. At the same time, other disciplines such as psychology extensively studied it. More specifically, social dilemma experiments allowed to identify several factors that impact cooperation [e.g. @VanLange2013]. For this reason, the current scoping review is aimed at gaining insight into cooperation in commons through social dilemma literature. In the next section, we will give an overview about the existing research about cooperation in commons, afterwards we will detail the research questions.

@@

However, research in different disciplines has often obtained opposite findings, namely that people can engage in collective actions to sustainably manage shared resources [@Poteete2010a]. Among these researches, the most important is Elinor Ostrom's seminal work [-@Ostrom1990], where she studied several real-life commons, some of them successfully managed by the community of users without the intervention of an external authority. Based on her observations, she established seven design principles that are present in all the successful commons, plus an eighth one for more complex cases.[^2]

@@

The first principle posits that boundaries are essential: it must be clear which is the shared resource, and who can benefit from it, otherwise, "no one knows what is being managed or for whom" (p. 91). Second, the rules must be congruent with the local conditions, i.e. they must reflect the specific attributes of the particular resource. Thirdly, individuals affected by the rules must be able to participate in modifying them. This ensure that the rules fit well to the local conditions and allows to promptly adapt them when needed. The fourth and fifth principles concern a monitoring and a graduate sanction system. Interestingly, these systems are successfully implemented by commoners themselves, with no need for an external institution. In fact, in order to know that the best strategy is to follow the rules, one must be sure that the others are also complying to them. For this reason, it is in everybody's self-interest to monitor other commoners. Similarly, the graduate sanction system can be easily self-regulated: even if punishing is usually profitable for the punisher, fines are naturally small for the first infraction and get higher only if the person persists in breaking the rules. In fact, since infractions are often due to extreme situations, punishers tend to be sympathetic because it could happen to them too. Linked to the previous principle, the sixth posits that people must have access to low-cost conflict resolution mechanisms, since, in a situation like a commons, disagreements between members are inevitable. Conflict resolution arenas give the rule-breaker the possibility to explain the mistake, and ensure that compliance to rules does not drop after every infraction. Finally, according to the seventh principle, external authorities should not challenge the commoners' right to self-organize and should recognize the commons' institutions.

@@

Secondly, on the experimental level, the laboratory study of social dilemmas largely contributed to the investigation of cooperation, by identifying several factors that impact it [e.g. @VanLange2013]. A typical constellation in these experiments (often also referred as "public good games" or "common resource experiments") is that people face a conflict between personal and collective interest. Each individual obtains a higher personal payoff with a non-cooperative, self-interested behaviour than with a social, cooperative one, independently from what others do. At the same time, everybody's payoff is higher if all cooperate than if all defect [@Dawes1980]. Social dilemma experiments are very useful for gaining insight into cooperation, because they are easily implemented in a laboratory, and provide a standard experimental paradigm to test under which conditions people cooperate [@Balliet2011]. In general, these studies demonstrated that people are able to cooperate, and that their behaviour is impacted by variables that should not play a role from a rational point of view [@Ostrom1998].

@@

Based on this evidence, the current paper synthesizes existing research about cooperation in social dilemmas, and provides a set of factors that impact cooperative behaviours in commons. This work will therefore lay the foundations to implement experimental and quantitative studies in real-life commons, which, in turn, will allow to gain insights about cooperation beyond artificial laboratory settings.

@@

<!--# PROBLEM: all my research questions are about social dilemmas, and the idea was to use this litterature to better understand cooperation in commons, however I also included papers that studied commons (in the search, one of the key words was "commons" => solution (?): in the methods section say that I also included commons literature for X,Y reasons (more completeness? see the rapport between the amount of SD and commons studies?)or, in your opinion, this doesn't cause any problem on the logic of the paper? -->

@@

@@

Our analysis identified five individuals factors that impact cooperation: gender, social status, group identification, values and personality traits, and trust. In the following sections, we describe their main effects on cooperation, and provide an overview of the moderators of each effect presented in the reviewed papers. A resume of the different individual factors is provided in Table 2, while more details about moderators are included in Appendix A.

+---------------------------------------------------------------+-----------------------+-------------------------------------------------------------------------------------------------+------------------------------------------------------------------+

@@

+===============================================================+=======================+=================================================================================================+==================================================================+
| Gender                                                        | *N*=11                | Ambiguous                                                                                       | -   Other participants' characteristics                          |
|                                                               |                       |                                                                                                 | -   Group composition                                            |

@@

+---------------------------------------------------------------+-----------------------+-------------------------------------------------------------------------------------------------+------------------------------------------------------------------+

@@

|                                                               |                       |                                                                                                 | -   Group composition                                            |
+---------------------------------------------------------------+-----------------------+-------------------------------------------------------------------------------------------------+------------------------------------------------------------------+

@@

|                                                               |                       |                                                                                                 | -   Intergroup competition                                       |

@@

+---------------------------------------------------------------+-----------------------+-------------------------------------------------------------------------------------------------+------------------------------------------------------------------+
| Social Value Orientation and other values/personality factors | *N*=5 (SVO)           | Pro-social individuals cooperate more than pro-self                                             | -   Incentives                                                   |
|                                                               |                       |                                                                                                 | -   Uncertainty about the number of members                      |
|                                                               | *N*=9 (other factors) | Pro-environmental values are positively correlated to cooperation                               | -   Deliberation                                                 |
|                                                               |                       |                                                                                                 | -   Inter- vs independent self                                   |
|                                                               |                       | Left-wingers are more cooperative than right-wingers                                            | -   Perceived social norms                                       |

@@

+---------------------------------------------------------------+-----------------------+-------------------------------------------------------------------------------------------------+------------------------------------------------------------------+
| Trust                                                         | *N*=10                | People with high levels of trust cooperate more than people with low levels                     | -   Degree of conflict between personal and collective interests |
|                                                               |                       |                                                                                                 | -   Uncertainty about others' intentions                         |

@@

On the group level, we identified four factors from the reviewed papers: incentives, communication, social norms and anonymity. As for the individual factors, in the following sections we detail the main effects of each factor, and we provide an overview of possible moderators. A resume of the main effects is provided in Table 3, while more details about the moderators in Appendix A.

+-----------------------+-----------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+
| Organizational factor | Analyzed papers | General effect on cooperation                                                  | Moderators                                                    |
+=======================+=================+================================================================================+===============================================================+
| Incentives            | *N*=18          | Punishment and reward systems have a positive effect on cooperation            | -   Cost of implementation                                    |
|                       |                 |                                                                                | -   Type of interaction                                       |
|                       |                 |                                                                                | -   Other participants' characteristics and group homogeneity |
|                       |                 |                                                                                | -   Context                                                   |
|                       |                 |                                                                                | -   Organization                                              |
|                       |                 |                                                                                | -   Type of incentives                                        |
+-----------------------+-----------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+
| Communication         | *N*=11          | Having the possibility to communicate with other members increases cooperation | -   Group size                                                |
|                       |                 |                                                                                | -   Type of communication                                     |
|                       |                 |                                                                                | -   Content                                                   |
|                       |                 |                                                                                | -   Timing                                                    |
+-----------------------+-----------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+
| Social norms          | *N*=8           | Cooperative social norms increase cooperation                                  | -   Anonymity                                                 |
+-----------------------+-----------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+
| Anonymity             | *N*=10          | Individuals cooperate more in non-anonymous situations than in anonymous ones  | -   Personal costs and benefits                               |
+-----------------------+-----------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+

@@

### Social norms

@@

The second identified factors is social status, and, once again, we obtained contradictory findings about its effect on cooperation. At the same time, our analysis revealed that members of low-status groups show solidarity with other low-status individuals, while this does not happen in high-status groups. This is consistent with the existing literature on social status. First, there are structural differences between high- and low-status group's dynamic, that make high-status members more individualistic than low-status [@Lorenzi-Cioldi2002]. Second, high-status individuals display more system justification (i.e. they perceive the social system as fair) and more Social Dominance Orientation (i.e. they have a preference for inequality between social groups) than low-status [@Caricati2012; @Vargas-Salfate2018]. This is negatively correlated with concern about others and altruism [@Pratto1994]. For this reason, social status must also be taken into account when investigating cooperation, since the solidarity dynamics described above influence individuals' behaviours.

Third, we found a strong positive effect of social identification: the more individuals identify with their group, the more they are likely to act for the group's good. <!--# question: when I recall results in the discussion, do I need to put again the citations? --> This is in line with the Social Identity Theory [@Tajfel1974], which posits that people's identity is also composed by their group affiliations. Therefore, the strongest the identification with a group, the more personal interests are aligned with group's ones. Also, within a social group, individuals perceive themselves as more similar to other members, and therefore they are more susceptible to adopt collective goals and behaviours [@Turner1984; @Fritsche2018]. Thus, for a group's success, its members' identification is essential: for instance, strongly identified individuals are less likely to leave a group in case of failure or difficulties [@Ellemers1997]. Given its importance, strengthen the commoners' social identification could significantly improve their cooperation for the commons' good. Moreover, priming a common social identity is quite simple [e.g. @Kramer1984; @Zhang2019]: this could allow to enhance cooperation in an easy and cheap way.

Fourth, Social Value Orientation also impacts cooperation. More specifically, individuals with a pro-social orientation cooperate more than those pro-self oriented. In fact, pro-social value more equality in outcomes, while for pro-self is the personal gain which is more important [@VanLange1999]. In addition to SVO, there are other values and personality traits which impact cooperation, such as political orientation, justice sensitivity, and self-control. Interestingly, although personality traits are usually stable, it is possible to modify values and attitudes, for example by making the participant elaborate about them [@Petty1995]. This technique could therefore be used to improve cooperation in commons.

@@

<!--# in the precent version I did not have a specific research question about how factors are connected to each-other, so this part fitted well: I took the results and completed them with related literatureNow that I do have a research question about the moderation, it feels strange to add new results in this part. Should I take here only the moderation effects identified in the results section? Or maybe should I start from what I found to further develop on other moderators? -->

@@

Concerning the review's limitations, we could identify three. First, there is a lack of representation of the global population. In fact, two thirds of the analyzed papers were studies conducted in Europe or in North America, and the fourteen reviews included were also mostly based on studies from Western countries. The current results apply therefore to Western societies and should not be generalized to other cultures. In fact, there are cultural differences in individualism and collectivism: generally, North American and European are more individualistic, while South American, African and Asian are more collective [@Triandis1989]. These differences affect the extent to which individuals define themselves as part of a group [@Trafimow1991] and, consequently, their behavior in cooperative situations [e.g. @Kuwabara2014]. It is therefore likely that, in different cultures, cooperation relies on different mechanisms: comparative studies should be conducted in order to reach a global understanding of cooperation.

Secondly, our aim was to use results of social dilemma researches to gain a better understanding of commons, therefore most of the included studies had a laboratory setting. In fact, this kind of setting is very useful to study social dilemmas because it provides a standard paradigm [@Balliet2011]. However, this does not allow to exactly reproduce the dynamics of a commons [@Henry2011; @Cole2010]: some elements such as cultural factors and real-life conditions affecting the decision-making process cannot be reproduced in lab experiments [@Janssen2015]. Therefore, this paper offers a good basis about elements influencing cooperation in commons, but future studies should confirm these results in real-life settings. Moreover, this review is not informative about the relative importance of each factor. To shed light on this topic, quantitative studies are needed.

@@

In conclusion, a successful commons relies on the cooperation of its members, but this topic has not yet been extensively studied. This review started to fill the gap, but further researches are still needed to address the limitations of the current paper and to reach a deeper understanding of this topic.
